%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% CV Nicolas Macé - Version consolidée pour maceparis.dev
% Template original: Awesome CV (https://github.com/posquit0/Awesome-CV)

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[11pt, a4paper]{article}

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Nicolas}{Macé}
\title{Software Developer · Graduate Engineer}
\address{Paris 75013, France}
\phone{(+33) 7 81 58 53 61}
\email{nicolas@maceparis.dev}
\homepage{maceparis.dev}
\social[linkedin]{nicomace}

%-------------------------------------------------------------------------------
\begin{document}

%-------------------------------------------------------------------------------
% SUMMARY
%-------------------------------------------------------------------------------
\section{Summary}

Backend Java Developer at AXA France with a strong focus on software craftsmanship, clean architecture, and modern development practices. I build robust, maintainable APIs using Java 21 and Spring Boot, deployed on Kubernetes (OpenShift) with event-driven architectures (Kafka).

Passionate about code quality and best practices: Test-Driven Development, clean code principles, functional programming concepts, and real-time/concurrent systems. I thrive in agile environments where continuous learning and technical excellence are valued. My engineering background combines hands-on experience with distributed systems, cloud-native architectures, and a keen interest in emerging technologies (blockchain, modern JVM languages).

Open to opportunities in innovative fintechs and scale-ups working with modern backend stacks (Java, Kotlin, functional programming) where craftsmanship and technical challenges are at the core.

%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------
\section{Education}

\cventry{2021 -- 2024}{Master's Degree in Computer Science -- Automated Systems (Engineering Degree)}{Polytech Angers, University of Angers}{Angers, France}{
  \begin{itemize}
    \item Software development, automation, modeling, embedded systems
    \item Projects in Java, Python, C/C++, SpringBoot, real-time systems
  \end{itemize}
}

\cventry{2019 -- 2021}{Integrated Preparatory Course -- Engineering Sciences (CPGE)}{Polytech Angers, University of Angers}{Angers, France}{
  \begin{itemize}
    \item General scientific curriculum: mathematics, physics, computer science, electromagnetism, algorithms
  \end{itemize}
}

%-------------------------------------------------------------------------------
% WORK EXPERIENCE
%-------------------------------------------------------------------------------
\section{Experience}

\cventry{Sep. 2023 -- Present}{Backend Java Developer (Full-Time since March 2024)}{AXA France}{Nanterre, France}{
  \begin{itemize}
    \item Developing backend services using Java Spring Boot (versions 17 and 21)
    \item Working on API orchestration and implementation using REST (OpenAPI/Swagger) and SOAP (WSDL)
    \item Deployment with Kubernetes containers on OpenShift (Red Hat) via Azure DevOps
    \item Working on a KYC project using Kafka
    \item Tools and practices: Maven, Git, Azure DevOps, ElasticSearch with Kibana, Sonar Pipelines
  \end{itemize}
}

\cventry{May 2023 -- Aug. 2023}{Test Automation Intern}{AXA France}{Nanterre, France}{
  \begin{itemize}
    \item Developed automated test solutions in VBA for functional testing
    \item Worked with Adobe Campaign, Selenium (Python), Ready API, and SOAP UI for API testing
  \end{itemize}
}

\cventry{Jan. 2023 -- Apr. 2023}{AI Developer Intern (YOLOv7 - Video Processing)}{Polytech Angers / Université du Mans}{Angers, France}{
  \begin{itemize}
    \item Created custom dataset and trained a YOLOv7 model to detect body parts in medical videos
    \item Implemented and evaluated the model using Python, analyzing accuracy and performance
  \end{itemize}
}

\cventry{Apr. 2022 -- Aug. 2022}{Web Developer Intern (MERN Stack)}{University of Bradford / xHumanity}{Bradford, United Kingdom}{
  \begin{itemize}
    \item Worked on xHumanity platform using React, Node.js (MERN Stack)
    \item Conducted blockchain development and research activities
  \end{itemize}
}

\cventry{Jun. 2020 -- Aug. 2020}{IT Support Technician (Internship + Fixed-term Contract)}{French Ministry of Ecology (DREAL Pays de la Loire)}{Nantes, France}{
  \begin{itemize}
    \item Secured network environments, prepared system images, sanitized sensitive data
    \item Provided technical support and troubleshooting for staff
  \end{itemize}
}

%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------
\section{Compétences}

\cvitem{Backend}{Java, Spring Boot, Kotlin, Node.js, Maven, Gradle}
\cvitem{Frontend}{React, JavaScript, TypeScript, HTML, CSS}
\cvitem{DevOps \& Cloud}{Docker, Kubernetes, OpenShift, Azure, Git, GitLab}
\cvitem{Data \& Messaging}{Kafka, Elasticsearch, Kibana, PostgreSQL, MongoDB, Redis}
\cvitem{Other Languages}{Python, C, C++, C\#, PHP, SQL, Go}

\cvitem{Languages}{
  English: C1 level certified, TOEIC 2022 score: 975/990. French: Native. German: Notions.
}

%-------------------------------------------------------------------------------
% EXTRACURRICULAR ACTIVITIES
%-------------------------------------------------------------------------------
\section{Extracurricular Activities}

\cventry{2013 -- Present}{Climbing}{}{}{
  \begin{itemize}
    \item Over 10 years of regular practice, demonstrating consistency and discipline
    \item Experience in supervising and coaching children
  \end{itemize}
}

\cventry{2015 -- Present}{Skydiving}{}{}{
  \begin{itemize}
    \item Holder of A, B, B2, and BPA licenses, with 250 jumps completed
  \end{itemize}
}

\cventry{}{Traveling}{}{}{
  \begin{itemize}
    \item Open-mindedness and adaptability through various trips abroad
  \end{itemize}
}

\end{document}
